---
title: "Basic_Linear_Regression_Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic_Linear_Regression_Model}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearRegressionModel)
library(bench)
library(stats)
```
##Basic Use
Visual statistical out put of the developed function to ensure code is properly running. 
The results are numerically equal within tolerance, confirming correctness.
```{r}
#Basic use of the developed function

data("data_linear_regression")
fit = linear_regression_model(data_linear_regression$x, data_linear_regression$y)
fit$coefficients
fit$R_squared

```
## Correctness Demonstration
We compare the coefficients and fitted values from our custom function against base R `lm()`. 
The results are numerically equal within tolerance, confirming correctness.
```{r}
#Correctness Check
# Check the correctness of the developed function against base R lm() function

lm_fit = lm(y ~ x, data = data_linear_regression)

# Compare coefficients numerically (allowing small numeric differences)
all.equal(unname(coef(lm_fit)), unname(fit$coefficients))

# Compare fitted values
all.equal(unname(fitted(lm_fit)), unname(fit$fitted))

#TRUE means functions match (within the small numerical differnces)

```
## Efficiency Demonstration
We benchmark our function against `lm()` using 100 iterations. 
The results show relative performance in terms of speed and memory usage.
```{r}
#Efficiency Check
# Checks the overall efficiency or computation time of the developed function against base R lm() function (bench mark)

bench::mark(
  linear_regression_model(data_linear_regression$x, data_linear_regression$y),
  lm(y ~ x, data = data_linear_regression),
  iterations = 100,
  check = FALSE # disables result equality check
)

```


